Predicting sales of newly published books

### 2015-08-25 paper.tex
contestando comentarios de Pablo
Revisado abstract corregido @fergunet

%%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%%
\author {
P.A. Castillo, A.M. Mora, J.J. Merelo, \\ A.J. Fern\'andez-Ares, P. Garc\'{\i}a-S\'anchez, M.G. Arenas
}
\institute{Department of Architecture and Computer Technology. CITIC \\
           University of Granada (Spain) \\
~\\
           e-mail: {\tt pacv@ugr.es}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

%% Many companies must face, as one of the most difficult tasks to
%% accomplish, new product sales estimation, since in many cases no
%% historical data to serve as guide is available. 
%% Moreover, some of them lack the knowledge about forecasting methods
%% and they can only make decisions based on the expert sales
  %% managers. 
% Eliminado esto.
When a new book is published the publishing house faces the problem of
how many books should be printed. Printing too many is the main issue,
since it implies a loss of investment due to inventory excess. That is
why in this paper we are tackling the problem on predicting sales to %FERGU: The problem ON predicting, no? ¡gracias!
print the right amount of books, doing so even before the book has
reached shelves, which is when printing occurs. 
%Thus, making inaccurate predictions may lead to erroneous decisions that result in excess production that will not be sold, or even to a production deficit.
%That is the publishing roll problem, in which publishing companies must estimate the number of volumes printed, taking care not to print more than they actually end up selling. Thus, an automatic prediction of book sales to estimate the publishing roll would be helpful for publishers.
% In the literature, different methods of sales prediction, mainly for
% the fashion industry are proposed. 
% Esto no pega nada en el abstract - JJ
%In these works, when sales are stable with a clear trend over time, the classical methods are a good choice. 
%However, in the case of new products, such as a new book publishing, classical methods do not work properly.
%In this paper, a rule-based decision method is proposed to address the
%problem of predicting the publishing roll.  
% It's not proposed. It just obtained the best result with WEKA. - JJ 
% Publishing roll? ¿Qué es? - JJ
%[Pedro] en la traducción de términos Antonio propone traducirlo como "print run". Lo pongo así.
In this paper, which works with data on published books for several years in
Spain, we first apply a data visualization and preprocessing strategy to find
out what are the relevant variables in the prediction of sales, and
then use standard data mining software to predict sales, and from them
deduce print-run, based on those variables. Our work discovers which
are the most relevant variables when predicting sales, and is
eventually able to predict sales with remarkable accuracy. In fact,
this method has been validated by the company that provided the data 
and incorporated in a business intelligence tool for publishing houses,
since the obtained models provide information on the decision process and
does not require human intervention either for the operation or for
interpretation.
\end{abstract}

>>>>

%%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%%
\author {
P.A. Castillo, A.M. Mora, J.J. Merelo, P. Garc\'{\i}a-S\'anchez, \\ A.J. Fern\'andez-Ares, M.G. Arenas, P. de las Cuevas
}
\institute{Department of Architecture and Computer Technology. CITIC \\
           University of Granada (Spain) \\
~\\
           e-mail: {\tt pacv@ugr.es}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
When a new book is published the publisher faces the problem of
how many books should be printed for delivery to bookstores. Printing too many is the main issue,
since it implies a loss of investment due to inventory excess. In this
paper we are tackling the problem of predicting total sales in order to %FERGU: The
                                %problem ON predicting, no? ¡gracias!  
% of predicting -  JJ
print the right amount of books, doing so even before the book has
reached shelves. 
In this paper, which works with several years of data on published books in
Spain, we first apply a data visualization and preprocessing strategy
in order to find
out what are the variables that have some impact on sales, and
then use standard data mining software to predict sales, and from them
deduce print-run, based on those variables. Our work focuses then in  discovering which
are the most relevant variables when predicting sales and is
eventually able to predict sales with remarkable accuracy. In fact,
this method has been validated by the company that provided the data 
and incorporated in a business intelligence tool for publishers,
since the obtained models provide guidance on the decision process of
publishing a book and do not require human intervention either for the operation or for
interpretation.
\end{abstract}
